Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-14 talk/iwtc11/paper.tex
drafted some conclutions

>>>>

\subsection{Conclutions}
In this paper we have studied loop invariant code motion during trace
compilation. We claim that loop peeling is a very convenient solution
here since it fits well with other trace optimizations. By peeling of
the first iteration and optimizing the resulting two iteration trace
as a single trace, several standard optimizations can be 
used unchanged. The only interaction needed between the loop peeling
and the other 
optimizations is during the constructing of the jump arguments
connecting the peeled of iteration (the preamble) with the loop body. This
approach 
turns standard optimizations such as redundant guard removal, heap
caching, pure operation reusage and allocation removals into loop
invariant code motion optimizations.

XXX: is ``loop body'' or ``peeled loop'' the preferable term?

By using several benchmarks we show that the proposed algorithm can
significantly
improve the run time of small loops containing numerical
calculations. 
At least in cases where there are not too many guard
failures. The standard way of handling guards that fail often is to 
trace a bridge from it back to the start of some previously compiled
loop. This is applicable here too. However the bridge will have to end
with a jump to the preamble, which lessens the impact of the 
proposed approach.
In many situations it is however possible to make the bridge
jump to the peeled loop instead. When and how this is possible will be
focus of future work.
